Supplementary material S2: Disturbance simulations

### 2018-07-13 S1-LL.Rmd
Draft 0.1.9005 Supplementary: RNE & LM

---
title: "Supplementary material S1: Leaf lifespan model"
date: '`r Sys.Date()`'
output:
  github_document: default
  bookdown::pdf_document2:
    number_sections: false
    toc: false
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

>>>>

---
title: "Supplementary material S1: Leaf lifespan model"
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: false
    toc: false
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

### 2018-07-13 S4-disturbance.Rmd
Draft 0.1.9005 Supplementary: RNE & LM

---
title: "Supplementary material S2: Disturbance simulations"
date: '`r Sys.Date()`'
output:
  github_document: default
  bookdown::pdf_document2:
    number_sections: false
    toc: false
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---

>>>>

---
title: "Supplementary material S2: Disturbance simulations"
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: false
    toc: false
csl: /home/sylvain/Documents/Bibliography/csl/mee.csl
bibliography: /home/sylvain/Documents/Bibliography/library.bib
link-citations: yes
---
